\subsection{Google Play}
Google Play is a digital distribution platform created by Google. It is used as an app store for Android devices as well as for music and ebook distribution. Since the goal of the project is to make apps for Android devices, we are using the Google Play to distribute the different apps. \citep{GooglePlay}

As it was our responsibility to maintain and control Google Play for this semester, we started by familiarizing ourselves with the different features provided by Google Play. We found that Google Play provides a lot of statistics for all the apps, like how many times the apps have been installed and how many that still have them installed. Google Play also allowed us to change which apps should be shown on the store and to change the descriptions of the apps. One thing we noticed when we looked at some of the descriptions was that a lot of them were very short and did not provide enough information about the apps, so the user would have trouble knowing the functionalities that the apps provide. Because of this, we decided to update the descriptions, making an English version of the descriptions in the process, and to update some of the pictures showing the apps to the user.

One kind of data that Google Play provided, which was very important, was the statistic about which version of Android the users were using. This allowed us to know that the apps currently should use the Android API version 15, because 22\% of the users were using Android version 4.0.3 - 4.0.4, which only supports API version 15 and below. \citep{API15}

\subsubsection{Alpha/Beta}
At the conclusion of last year's work on the Giraf project, all the apps from the project were uploaded to Google Play. This meant that the apps became available for the users, and that data about crashes would be sent to Google Play and Google Analytics. The initial releases were plagued by crash issues and other errors. Some of these issues were attributed to certain applications crashing when trying to use other apps.

To avoid releasing unstable versions on Google Play, while still being able to test the apps through Google Play, it was decided to add an alpha and beta release version to Google Play. The alpha and beta versions fulfill the same role of ensuring that builds were stable before release, but they are updated differently. The alpha version would be updated whenever a new build is uploaded onto the Jenkins server and it passes the automatic tests to ensure it does not break the build. If it passed all of that, this new build will replace the alpha version available on Google Play. The beta version should be updated at each sprint end to the newest alpha build. There were not any plan for when to update the official release, but it follows that stable beta versions can be released officially.

For the work in this implementation of alpha and beta versions, we found a plug-in for Jenkins that could be used to make the uploading of alpha and beta versions automatic, as well as providing the information the server needs to upload to Google Play. The plug-in and information was then passed on to the group responsible for the Jenkins server, so they could implement the automated upload.