\section{Colaboration between product owners}
\textit{This section will cover the collaboration work taht was done between the three different product owner groups.}

AS there where three different groups that where product owners in the project, some of the task and information was shared between us. This included user stories, tasks, and the information related to sprint planning and sprint ends.

\subsection{Sprint ends and sprint planning}
During each sprint a number of user stories was given to the different product owners, but it was not always the product owners for the correct subproject that received these user stories. It was therefore decided  to have a meeting between the product owners between the sprint ends and sprint plannings, where we shared the user stories we had and discussed if there where any other user stories that where needed or if some of the user stories should be formulated better. We then distributed the user stories to the backlog for the subproject they belonged to, so that the user stories was ready to be presented at the sprint planing for that subproject.

\subsection{Product backlog and release backlog}
Because all product owners where responcible for making a backlog and a release log for the user stories, we gathered together to collect them all in one place. This meant that all the user stories should be formulated in a similar way and that at least one from each group needed to be present, so that all user stories for the three subproject was included in the document.

In the process of making the document our group was the main contributer, in the sence that it was our respncibility to make the pdf document that should be included on the Redmine Wiki page, for the next years students. A copy of this document can be found in Appendix \ref{Appendix_secBacklog}.