\section{Package Solution} \label{Sprint4_PackageSolution}
\textit{The external customers requested a simple and easy way to install and run every app in the Giraf-system. This section will cover our approach to problem, and we present a possible solution.}

\subsection{Motivation}
As the external customers are not technically advanced, we should make the download and installation process for the apps as simple as possible. One thing that the customers specifically requested was the ability to download and install the entire Giraf-system by just downloading one app. This would also make it easier to use the system for people new to the system as they would then not have to download 10 separate apps to use it.

\subsection{Approach}
The first thing we did was to research whether Google Play had any incorporated methods to combine apps or at least download and install multiple apps from the same Google Play store-page. From our research we found that Google have not made anything that can accomplish these things.
As Google Play does not have the functionality to do what we need, we have to combine the apps ourselves. Here there are two approaches, one would be to code a single app, which would then have the functionality of all current and possible future apps. The other approach would be to modify the current launcher and add the other apps as libraries in a similar manner to how ‘Pictosearch’ is used.
The first approach would make it much harder to split up the work to multiple groups, which would go against the scrum-process used in the project. Using the second approach would solve this problem and as such that would be our approach to the problem.


During a semester meeting with the other groups, it was decided that making a package solution where every app were combined to one, were not a high priority, and it would take more time then there were left for this sprint. The consequence and approaches to having one complete app which include all the apps, will be taken up in the chapter for next year's students.