\section{Summary} 
\textit{This section is a short description of what we did in the 4th sprint, and which user stories that followed over to the next sprint.}\\

The main goal of the 4th sprint was to make the project ready for being taken over by other group next year.


\textbf{App name consistency}
We managed to make the app names consistent and understandable for all apps except for one, with was the “weekschedule” with instead got the name “ugeplan”. 

\textbf{Guides}
For the sprint we made a guide for the groups next year. This included a guide for the use of Google Play and a Starter guide for how to instal and run the basic tools in the project. In addition to making these guides we also made a document that described and referenced all the guides from the groups in the build and deploy subproject.

\textbf{Picosearch to library}
In the sprint we made the final changes in making pictoseach into a library and made it so that all the apps used the library instead of the service app version of pictosearch.

\textbf{App bundle}
Found that Google Play do not support the use of app packages. Because of this it would only be possible to make one place where the user can get all the in one place by collecting all the apps into one, but this was decided to be postponed to next year.

For the last sprint we finished all our user stories, which is also the most optimal since this is the last sprint, and any further work would not be done by us, but instead from one of the next year groups.