\section{Summary} 
\textit{This section is a short description of what we did in the 2nd sprint, and which user stories that followed over to the next sprint.}\\

The main goal for the 2nd sprint was to reform the structure of the project, with the goal of improving the build time of apps and improving the structure of the git repositories.


\textbf{Dependencies}
We were given the task of finding dependencies for the apps and libraries, for this we found all the dependencies and listed them. To improve the overview of the dependencies we made a graph for app-library, library-library, and app-app dependency. These graphs was shared with the rest of the groups by making a redmine wiki page.

\textbf{Standalone}
In the user story to make an standalone apps standalone we started by finding out what functionality the app would need to be able to function on there own. For this we found that we would need to make an library that included these functionalities, with then is included in all the apps.

\textbf{Build structure}
When building apps in the project the build time was very long because all libraries were built recursively. To improve this we incorporated the use of .aar files in the build process. This lead to a change in the number of build from exponential number of build, to a linear growth, in relation to the number of libraries.

For the 2nd sprint we did not complete all the task that were assigned to us. The tasks we did not complete were standalone app and the making of a core library. These task was not finished because the proved to have a lot more work to them. We continued working with the core library in the 3rd sprint, but postponed the standalone app since the app would require the core library before any more work could be done.